% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[letterpaper]{article}
\usepackage[margin=1in]{geometry} % Set 1 inch margins on all sides
\usepackage{fancyhdr} % For customizing headers and footers
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{thomas-james-l.-francis}{%
\begin{center}
\section{Thomas James L. Francis}
\end{center}
\label{thomas-james-l.-francis}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1358}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1728}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.1975}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.4938}}@{}}
\toprule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Norwalk, CT & (203)-278-1760 & toj320@gmail.com &
https://thomasjamesfrancis.com/portfolio \\
\end{longtable}

~

12/6/2023

~

Dear HR at Summus,

~

I am interested in the opening for \textbf{Software Engineer, Fullstack}
at Summus.

Owing to my experience as an Application Support Analyst for MHK's
medicare healthcare platform, I believe that the U.S. Healthcare system
is in dire need of change and that Summus's physician-focused platform
is a step in the right direction.

I am a full stack web developer with five years of programming
experience. Alongside a certificate in Full Stack Web Development from
Holberton (a rigorous 18-month coding bootcamp), I have a B.S. in
Chemistry from the University of Connecticut, where I attended with
honors on full scholarship and earned the prestigious Roland Award for
an outstanding senior thesis.

My most recent employment was as a full stack developer for Synergy
Corporate Technologies, where I learned the basics of software
consultancy through direct communication with clients. There I became
familiar with the Microsoft tech stack, which included technologies such
as Azure, SharePoint, and PowerShell. While building Microsoft apps for
clients, my full stack skills were put to use in building the frontend
of their proprietary ticketing from scratch with React and Redux. My
manager regularly praised me for my hard work, diligence, and technical
achievements.

I am excited to apply my education, skills, and work ethic to your fine
organization.

Please let me know a convenient time to discuss this possibility.

Thank you very much.

~

~

~

Sincerely,

Thomas Francis

\end{document}
